---
title: 'Worksheet #5'
author: "Fabio Tran"
date: "2/11/2022"
output:
  html_document: default
---

## Question 1

```{r}
library("ISLR2")
data("Credit")
dim(Credit)
names(Credit)
```

## Question 2

```{r}
my_logist_regr = glm(Student ~ Income + Balance + Cards, data = Credit, family = binomial)
summary(my_logist_regr)
```

## Question 3

With 95% confidence, the variables that have strong evidence of a relationship with student status are Income and Balance. 
```{r}
my_logist_regr = glm(Student ~ Income + Balance, data = Credit, family = binomial)
summary(my_logist_regr)
```

## Question 4

```{r}
newdata = data.frame(Balance = c(1200), Income = c(23000))
predict(my_logist_regr, newdata, type = "response")
```

## Question 5

```{r}
my_prob_results = predict(my_logist_regr, Credit, type = "response")
```

## Question 6

```{r}
my_classification = ifelse(my_prob_results > 0.50, "Yes", "No")
```

## Question 7

```{r}
my_classification
```

## Question 8

```{r}
table(my_classification, Credit$Student)
```

## Question 9

The training error rate is 39/400 which is 9.75 percent. 

## Question 10

```{r}
mean(my_classification != Credit$Student)

```

## Question 11

The best rate I was able to get by lowering the probability threshold was 7.75 percent. 
```{r}
my_classification = ifelse(my_prob_results > 0.35, "Yes", "No")
table(my_classification, Credit$Student)
mean(my_classification != Credit$Student)
```

## Question 12

```{r}
v = sample(1:400, 200)
v = sort(v)
```

## Question 13

```{r}
Credit.train = Credit[v, ]
Credit.test = Credit[-v, ]
```

## Question 14

```{r}
my_logist_regr = glm(Student ~ Income + Balance, data = Credit.train, family = binomial)
summary(my_logist_regr)
```

## Question 15

```{r}
my_prob_results.train = predict(my_logist_regr, Credit.train, type = "response")
my_prob_results.test = predict(my_logist_regr, Credit.test, type = "response")
```

## Question 16

```{r}
my_classification_train = ifelse(my_prob_results.train > 0.50, "Yes", "No")
mean(my_classification_train != Credit$Student)
my_classification_test = ifelse(my_prob_results.test > 0.50, "Yes", "No")
mean(my_classification_test != Credit$Student)
```

## Question 17

With a threshold of 0.50, for the training error rate I got `r mean(my_classification_train != Credit$Student)` and for testing error rate I got `r mean(my_classification_test != Credit$Student)`. 
```{r}
my_classification_train = ifelse(my_prob_results.train > 0.35, "Yes", "No")
mean(my_classification_train != Credit$Student)
my_classification_test = ifelse(my_prob_results.test > 0.35, "Yes", "No")
mean(my_classification_test != Credit$Student)
```
When I lowered the threshold to 0.35, for the training error rate I got `r mean(my_classification_train != Credit$Student)` and for testing error rate I got `r mean(my_classification_test != Credit$Student)`.

## Question 18

```{r}
library(class)
standardized_credit = scale(Credit[, c("Income", "Balance")])
set.seed(1)
v = sort(sample(1:400, 200))
train.X = standardized_credit[v, ]
test.X = standardized_credit[-v, ]
train.Y = Credit$Student[v]
test.Y = Credit$Student[-v]
set.seed(1)
knn.pred = knn(train.X, test.X, train.Y, k = 3)
m = mean(test.Y != knn.pred)
print(m)
```

## Question 19

After trying various values of K, a value of 5 is a good choice as it yields a test error rate of 9 percent. 
```{r}
library(class)
standardized_credit = scale(Credit[, c("Income", "Balance")])
set.seed(1)
v = sort(sample(1:400, 200))
train.X = standardized_credit[v, ]
test.X = standardized_credit[-v, ]
train.Y = Credit$Student[v]
test.Y = Credit$Student[-v]
set.seed(1)
knn.pred = knn(train.X, test.X, train.Y, k = 5)
m = mean(test.Y != knn.pred)
print(m)
```

## Question 20

The prediction for that person being a student is no. 
```{r}
newTest.X = data.frame(Income = c(22000), Balance = c(1200))
knn.pred = knn(train.X, newTest.X, train.Y, k = 5)
knn.pred
```



