---
title: 'Homework #7'
author: "Fabio Tran"
date: "3/23/2022"
output: html_document
---

## Question 2
My work for this question was done on a Google Document.

[Link to Google Document](https://docs.google.com/document/d/1YmtJxVWigUZ03VDMzzwcX_bBrWd_9Yp2mKB3szaR4_U/edit?usp=sharing)

## Question 7

```{r}
library("ISLR2")
data("Auto")
```

**Part A**

```{r}
mpg_median = median(Auto$mpg)
mpg01 = ifelse(Auto$mpg > mpg_median, 1, 0)
Auto$mpg01 = as.factor(mpg01)
Auto$name = NULL
```

**Part B**

```{r}
library(e1071)
set.seed(1)
cv_linear = tune(svm, mpg01 ~ . -mpg, data = Auto, kernel = "linear",  ranges = list(cost = c(0.001, 0.01, 0.1, 1, 5, 10, 100)))
summary(cv_linear)
best_model = cv_linear$best.model
summary(best_model)
```

When cost equals 0.001 the cross validation error is 0.13525641.

When cost equals 0.01 the cross validation error is 0.08923077.

When cost equals 0.1 the cross validation error is 0.09185897.

When cost equals 1 the cross validation error is 0.08435897.

When cost equals 5 the cross validation error is 0.08948718.

When cost equals 10 the cross validation error is 0.08948718.

When cost equals 100 the cross validation error is 0.08692308.

The best value for the cost parameter is 1 because in the model it yields the lowest cross validation error of 0.08435897. This cost value has 88 support vectors associated with it.

**Part C**

```{r}
set.seed(2)
cv_polynomial = tune(svm, mpg01 ~ . -mpg , data = Auto, kernel = "polynomial", ranges = list(cost = c(0.001, 0.01, 0.1, 1,5,10), degree = c(2,3,4)))
summary(cv_polynomial)

set.seed(3)
cv_radial = tune(svm, mpg01 ~ . -mpg , data = Auto, kernel = "radial", ranges = list(cost = c(0.001, 0.01, 0.1, 1, 5, 10), gamma = c(0.001, 0.01, 0.1, 1, 5, 10)))
summary(cv_radial)
```

When kernel = "polynomial" the best parameters are when cost equals 5 and degree equals 3 since in the model the cross validation error is the lowest at 0.08141026.

When kernel = "radial" the best parameters are when cost equals 1 and gamma equals 1 since in the model the cross validation is the lowest at 0.07153846.

**Part D**

```{r}
linear_svm_model = svm(mpg01 ~ . , data = Auto, kernel="linear", cost = 1)
plot(linear_svm_model, Auto, mpg ~ cylinders)
plot(linear_svm_model, Auto, mpg ~ displacement)
plot(linear_svm_model, Auto, mpg ~ horsepower)
plot(linear_svm_model, Auto, mpg ~ weight)
plot(linear_svm_model, Auto, mpg ~ acceleration)
plot(linear_svm_model, Auto, mpg ~ year)
plot(linear_svm_model, Auto, mpg ~ origin)

polynomial_svm_model = svm(mpg01 ~ . , data = Auto, kernel="polynomial", cost = 10, degree = 3)
plot(polynomial_svm_model, Auto, mpg ~ cylinders)
plot(polynomial_svm_model, Auto, mpg ~ displacement)
plot(polynomial_svm_model, Auto, mpg ~ horsepower)
plot(polynomial_svm_model, Auto, mpg ~ weight)
plot(polynomial_svm_model, Auto, mpg ~ acceleration)
plot(polynomial_svm_model, Auto, mpg ~ year)
plot(polynomial_svm_model, Auto, mpg ~ origin)

radial_svm_model = svm(mpg01 ~ . , data = Auto, kernel="radial", cost = 1, gamma = 1)
plot(radial_svm_model, Auto, mpg ~ cylinders)
plot(radial_svm_model, Auto, mpg ~ displacement)
plot(radial_svm_model, Auto, mpg ~ horsepower)
plot(radial_svm_model, Auto, mpg ~ weight)
plot(radial_svm_model, Auto, mpg ~ acceleration)
plot(radial_svm_model, Auto, mpg ~ year)
plot(radial_svm_model, Auto, mpg ~ origin)
```

